CSD, Disjoint components and trayectory detection

### 2019-11-19 ArticuloCSDyCM/Paper03.tex
trazos estriado listo

\usepackage{caption}

@@

@@

@@

\begin{figure}[H]
 \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.7\textwidth]{Figuras/lfpestriado.pdf}
  \caption[tu abuela]{
    \begin{intension}
      Esta figura contrasta mucho con la figura \ref{lfpevocada}.
      Bajo la misma representación, tenemos muy claro que no hay
      estructuras discernibles. Sin embargo, requiere una serie de trazos
      bien escogidos para saber si hay actividad relevante.
    \end{intension}
    LFP stratial Tissue, some samples. There are no discernible
    structures. The apparent active set at the lower left corner
  is an artifact due to some bubbles in the experiment.}
\end{figure}

>>>>

\usepackage{caption}
\usepackage{subcaption}

@@

In the figure \ref{trazselectevo} we show a sample of the LFP
raw traces and how they appear in the CSD representation. A diagram
over a frame of the LFP is shown delimiting the region of interest and
some selected electrodes.

@@

\begin{figure}[H]
   \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figuras/lfpcuadrodiagramaevocado.pdf}
        \caption{Select Electrodes}
        \label{fig:sel}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.2\textwidth}
        \includegraphics[width=\textwidth]{Figuras/lfpevocselect_3R7.pdf}
        \caption{LFP, Raw}
        \label{fig:lfpraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.2\textwidth}
        \includegraphics[width=\textwidth]{Figuras/csdevocselect_3R7.pdf}
        \caption{CSD}
        \label{fig:csd}
    \end{subfigure}
    \caption{
      \begin{intension}
        Mostremos unos cuantos trazos de la medida cruda y su representación
        en el espacio CSD, para establecer lo adecuado del experimento.
      \end{intension}
      Electrode signal across some selected electrodes over the CA3 region.
      We show in subfigure \ref{fig:sel} a frame of the raw signal in the same color
      scale as fig. \ref{lfpevocada}. The GD and CA3 structures appear as red stains,
      their general shape recognizable. In subfigure \ref{fig:lfpraw}
      the raw traces of the selected electrodes are shown, and in \ref{fig:csd} the
      csd traces come along for comparision. In this last subfigure the
      vertical scale is in arbitrary units. }
  \label{trazselectevo}
\end{figure}

@@

\begin{figure}[H]
 \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.7\textwidth]{Figuras/lfpestriado.pdf}
  \caption[tu abuela]{
    \begin{intension}
      Esta figura contrasta mucho con la figura \ref{lfpevocada}.
      Bajo la misma representación, tenemos muy claro que no hay
      estructuras discernibles. Sin embargo, requiere una serie de trazos
      bien escogidos para saber si hay actividad relevante.
    \end{intension}
    LFP stratial Tissue, some samples. There are no discernible
    structures. The apparent active set at the lower left corner
    is an artifact due to some bubbles in the experiment.}
  \label{cuadestriado}
\end{figure}

\begin{figure}[H]
   \centering
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{Figuras/mapestriado_1004AP.pdf}
        \caption{A Frame}
        \label{maptraz:map}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=\textwidth]{Figuras/trazosestriado_1004AP.pdf}
        \caption{Traces}
        \label{maptraz:traz}
    \end{subfigure}
    \caption{
      \begin{intension}
        Mostramos aquí unos trazos ejemplares para asegurarnos de la
        calidad del experimento.
      \end{intension}
      Selected Traces of the Stratial Tissue. A frame such as the ones
      in figure \ref{cuadestriado} shows the location of the selected electrodes,
    which where algorhytmically chosen.}
